\begin{exercise}{6}
There are 20 people at a chess club on a certain day. They each find opponents and
start playing. How many possibilities are there for how they are matched up, assuming
that in each game it does matter who has the white pieces (in a chess game, one player
has the white pieces and the other player has the black pieces)?
\end{exercise}

\begin{proof}
    In order to form the teams, we can start by choosing who plays white. The order does not matter at this point since the games themselves are not ordered - so it is irrelevant if a player joins the first or the third game, for example. There are $20 \choose 10$ possible choices for the players who play white.

    We then need to match the players who play white with the remaining 10 players who will play black. Given a choice of players who play white, we can form $10!$ games by permuting the players who play black.

    Putting the two together, we end up with $20 \choose 10 $ $  10! = 184756 \cdot 3628800 = 670442572800$  games.

    \vspace{2em}

    For a different approach, observe that there will always be 10 pairs formed from the 20 people. Now, take the 20 people and form a first pair. There are $20 \choose 2$ ways to perform this (selection, without order within each pair). We block out those two people from being reselected: there are now 18 people left to form the subsequent pair. Perform such a process of generating pairs, until exhaustion. Symbolically, this all entails: 
    
    $${20 \choose 2} \cdot{18 \choose 2} \cdot \dots \cdot {2 \choose 2}$$

    We must now remove the overcounted. Given there are 10 pairs (corresponding to the 10 factors above), the overcounting corresponds to the ordering of each pair amongst one-another. This entails:

    $$\frac{ {20 \choose 2} \cdot{18 \choose 2} \cdot \dots \cdot {2 \choose 2}}{10!}$$

    Finally, we must incorporate the significance of playing white or black, within each pair. This entails a "binary counting" factor of $2^10$. Finally, we arrive at:
    
    $$2^{10}\frac{ {20 \choose 2} \cdot{18 \choose 2} \cdot \dots \cdot {2 \choose 2}}{10!} = 670442572800$$
    
\end{proof}


